Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-29 journal/article.tex
Training

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Pilot programs and other piloting   & 
                P6, P7, P8, P9, P10, P11, P14, P16, P18, P22, P23, P24,
                P27, P29, P36, P38, P40, P41, P43, P45, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Activities in the organization aiming to create change}
    \label{table:transformation_activities}
\end{table}

How many?

Reasons for piloting

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Pilot programs and other piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\  %22
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_activities}
\end{table}

% Training

As the organization is changing it is necessary to train people so they get
familiarity with the new model that is being pursued. The majority of cases
described the use of training in the transformation.
Most typically the change leaders and pilot teams were the first to attend
formal training on agile development. Management was also usually among the
first ones to receive agile training. In some cases particularly management
received more in-depth training [P11, P16, P24]. In addition to providing an initial
understanding of agile it was considered important that the key people get a
common understanding of the method [P11, P24, P39].

After key people had attained knowledge on agile, and pilot teams had possibly
tested the methods, other teams received training on the new development model.
In some cases the training of development teams was described to be brief [P11,
P16, P20]. Other cases implemented a full day workshop [P18, P23, P32, P41,
P45], and some organizations invested even in multi-day training [P9, P19, P37,
P49].
The reduced training for engineers was compensated with coaching during ongoing
projects [P11].

Several cases mentioned that the first introductory events were held by known
industry experts [P3, P19, P25, P27, P30, P46]. External consultants were also
often used as trainers [P18, P25, P40, P41, P49, P51]. In some cases a limited
number of people with agile knowledge was first trained or acquired, and later
the training was arranged with internal resources [P3, P11, P24, P25, P41, P46,
P49, P51].
The training curriculum was evolving as trainers improved and learned the needs
of the organization [P6]. In some cases training workshops was initially
tailored to suite the needs of the project [P23].

Training was considered as important. Training was reported to make a difference
between success and failure of teams [P6].
It became clear that training was necessary to retain an agile culture [P19].
Training was also described to increase the general interest towards using agile
methods [P3].
There were also some negative observations related to training. Atlas [P3]
describes that the insights gained from training were less than anticipated
[P3]. In another case product managers did not receive training and they stuck
in old ways of managing, which jeopardized the transformation [P35].

% Some training included simulation workshops [P40, P41].
% Hands-on workshops [P46].

Why is piloting started?

Who?

What amount of piloting is applied?

Did it work?

@@
